---
title: "IDS investigation worksheet"
author: "by Fighting Wolves: Jiayi Wan, Wanfang Zhen, George Zhu, Yifu Li & Yunrui Lyu"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
library(tidyverse)
library(dplyr)

```

# season--season number
# race_num--sequential number of race within the season
# race_name--Race report race name. Two part races have "race 2" added to it.
# race_date--Date of race, YYYY-MM-DD
# driver--driver names, from race reports, but standardized to be consistent
# car--car number
# team--team name per race report
# team_group--subjectively grouped teams, favoring their Season 6 team; allows continuity from sponsorship changes as well as team evolution (Renault/Nissan)
# rank--rank description, directly from race report
# rank_num--rank, numeric. Always numeric, even including retirements and unclassified finishes.
# grid--Starting grid position. Includes pre-race penalties, so not always indicative of strict qualifying results. Will not indicate starts from pit lane. Simply numeric.
# laps--number of laps completed. Taken directly from race reports.
# time_retired--Description that changes per type of finish. Final finish time for the leader. Number of seconds behind for those on the same lap. Number of laps behind, if relevant. Description of retirement, if relevant.
# pts_rank--points earned, based on finish position.
# pts_pole--points earned for qualifying on pole. Penalties can cause this to be slightly different than grid:1 (e.g. 2019 Monaco).
#pts_bonus--points earned through other bonuses such as fastest lap and fastest time in qualifying group stage.
#points--total Championship points earned. Sum of pts_rank, pts_pole, pts_bonus. Used to validate against final season standings.

```{r load-data}
FERR <- read_csv("data/formula_e_race_results.csv")
problems()
View(FERR)

```
#total points of selected driver in specific season
points_selected_driver <- function(x, y) {
  result <- FERR %>%
    filter(x == season, y == driver) %>% 
    summarise(TotalPoints = sum(points, na.rm = TRUE))
  return(result)
}

#total points of selected team
points_selected_team <- function(x, y) {
  result <- FERR %>%
    filter(x == season, y == team_group) %>% 
    summarise(total_points = sum(points, na.rm = TRUE))
  return(result)
}

#list of total points 
points_driver <- function(x){
  result <- 
  FERR %>%
    filter(x == season) %>%
    group_by(driver) %>%
    summarise(total_points = sum(points, na.rm = TRUE))
  return(result)
}

#list of total points in teams
points_team <- function(x){
  result <- 
  FERR %>%
    filter(x == season) %>%
    group_by(team_group) %>%
    summarise(total_points = sum(points, na.rm = TRUE))
  return(result)
}
points_team("1")
#visualization of total points earned by each team groups in different seasons 
#using season 1 as an example
ggplot(points_team("1"),
       mapping = aes(y = team_group, x = total_points)) +
  geom_bar(stat = "identity") + 
  labs(
    x = "Total Points", 
    y = "Team Group",
    title = "Total Points Earned By Each Team Group")

#visualization of total points earned by each drivers
ggplot(points_driver("1"),
       mapping = aes(driver, x = total_points)) +
  geom_bar(stat = "identity") + 
  labs(
    x = "Total Points", 
    y = "Driver",
    title = "Total Points Earned By Each Driver")

