---
title: "IDS investigation worksheet"
author: "by Fighting Wolves: Jiayi Wan, Wanfang Zhen, George Zhu, Yifu Li & Yunrui Lyu"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidymodels)
```


```{r load-data}
FERR0 <- read_csv("data/formula_e_race_results.csv")
#the original dataset
FERR <- read_csv("data/formula_e_race_results.csv") %>% 
  # Removing rows where points is 0
  filter(points != 0)
problems()
View(FERR)
View(FERR0)
```


```{r summary of best drivers}
# Calculate total points for each driver over each season
driver_season_points <- FERR %>%
  group_by(season, driver) %>%
  summarise(total_points = sum(points), .groups = 'drop')

# Find the driver with the best total points for each season
best_drivers_by_season <- driver_season_points %>%
  group_by(season) %>%
  filter(total_points == max(total_points)) %>%
  ungroup()

# Display the summary table with the best drivers by season and their total points
best_drivers_by_season_summary <- best_drivers_by_season %>%
  select(season, driver, total_points)

best_drivers_by_season_summary

```


```{r list of driver}
points_driver <- function(x){
  result <- 
  FERR %>%
    filter(x == season) %>%
    group_by(driver) %>%
    summarise(total_points = sum(points, na.rm = TRUE)) %>%
    arrange(desc(total_points))
  return(result)
}

for(i in 1:7)
  print (points_driver(i))


```


```{r driver visualization}
ggplot(points_driver("2"), aes(x = reorder(driver, total_points), 
                               y = total_points, 
                               fill = total_points)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = total_points), 
            position = position_dodge(width = 0.9), 
            hjust = -0.1, 
            vjust = 0.25, 
            size = 3) +
  scale_fill_gradient(low = "skyblue", high = "purple") +  # Gradient color based on total points
  labs(
    x = "Driver", 
    y = "Total Points",
    title = "Total Points Earned By Each Driver in Season 1"
  ) +
  theme_minimal() +  # A clean, minimal theme
  theme(
    plot.title = element_text(hjust = 0.5), # Center the title
    axis.text.x = element_text(hjust = 1),  # Rotate x-axis labels for better readability
    legend.title = element_blank() # Remove the legend title
  ) +
  coord_flip() # Flip the coordinates to make a horizontal bar plot

```


```{r}
freq_season_1 <- FERR %>%
  filter(season == "1") %>%
  select(driver) %>%
  table() %>%
  as.data.frame()
  View(freq_season_1)
  
  freq_season_2 <- FERR %>%
  filter(season == "2") %>%
  select(driver) %>%
  table() %>%
  as.data.frame()
  View(freq_season_2)
  
  freq_season_3 <- FERR %>%
  filter(season == "3") %>%
  select(driver) %>%
  table() %>%
  as.data.frame()
  View(freq_season_3)
  
  freq_season_4 <- FERR %>%
  filter(season == "4") %>%
  select(driver) %>%
  table() %>%
  as.data.frame()
  View(freq_season_4)
  
  freq_season_5 <- FERR %>%
  filter(season == "5") %>%
  select(driver) %>%
  table() %>%
  as.data.frame()
  View(freq_season_5)
  
  freq_season_6 <- FERR %>%
  filter(season == "6") %>%
  select(driver) %>%
  table() %>%
  as.data.frame()
  View(freq_season_6)
  
  
 selected_season <- FERR %>%
  filter(season == "1") %>%
  group_by(driver) %>%
  summarize(avg_points = mean(points, na.rm = TRUE))

print(selected_season) 

selected_season_with_freq <- merge(selected_season, freq_season_1, by = "driver", all.x = TRUE)
selected_season_with_freq$driver <- reorder(selected_season_with_freq$driver,
selected_season_with_freq$avg_points, FUN = function(x) -x)




ggplot(selected_season_with_freq, aes(x = driver, y = avg_points)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(
    x = "Driver",
    y = "Average Points",
    title = "Average Points per Driver in Season 1"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_x_discrete(labels = function(x) paste(x, " (Freq:", selected_season_with_freq$Freq[match(x, selected_season_with_freq$driver)], ")"))
```