---
title: "IDS investigation worksheet"
author: "by Fighting Wolves: Jiayi Wan, Wanfang Zhen, George Zhu, Yifu Li & Yunrui Lyu"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
library(tidyverse)
library(dplyr)

```


```{r load-data}
FERR <- read_csv("data/formula_e_race_results.csv") %>% 
  # Removing rows where points is 0
  filter(points != 0)
problems()
View(FERR)

```

```{r selected driver}
#total points of selected driver in specific season
points_selected_driver <- function(x, y) {
  result <- FERR %>%
    filter(x == season, y == driver) %>% 
    summarise(TotalPoints = sum(points, na.rm = TRUE))
  return(result)
}
points_selected_driver("1", "Nelson Piquet Jr.")
```

```{r selected team}
#total points of selected team
points_selected_team <- function(x, y) {
  result <- FERR %>%
    filter(x == season, y == team_group) %>% 
    summarise(total_points = sum(points, na.rm = TRUE))
  return(result)
}
```

```{r list of driver}
#list of total points 
points_driver <- function(x){
  result <- 
  FERR %>%
    filter(x == season) %>%
    group_by(driver) %>%
    summarise(total_points = sum(points, na.rm = TRUE)) %>%
    arrange(desc(total_points))
  return(result)
}
points_driver("1")
```

```{r driver visualization}
#visualization of total points earned by each drivers
ggplot(points_driver("1"),
       mapping = aes( reorder(driver, total_points), x = total_points)) +
  geom_bar(stat = "identity") + 
  labs(
    x = "Total Points", 
    y = "Driver",
    title = "Total Points Earned By Each Driver")
```

```{r list of team}
#list of total points in teams
points_team <- function(x){
  result <- 
  FERR %>%
    filter(x == season) %>%
    group_by(team) %>%
    summarise(total_points = sum(points, na.rm = TRUE)) %>%
    arrange(desc(total_points))
  return(result)
}
points_team("1")
```

```{r team visualization}
#visualization of total points earned by each team in different seasons
#using season 1 as an example
ggplot(points_team("1"),
       mapping = aes(y =  reorder(team, total_points), x = total_points)) +
  geom_bar(stat = "identity") + 
  labs(
    x = "Total Points", 
    y = "Team",
    title = "Total Points Earned By Each Team")
```

```{r list of teamgroup}

points_teamgroup <- function(x){
  result <- 
  FERR %>%
    filter(x == season) %>%
    group_by(team_group) %>%
    summarise(total_points = sum(points, na.rm = TRUE)) %>%
    arrange(desc(total_points))
  return(result)
}
points_teamgroup("1")
```

```{r teamgroup visualization}
#visualization of total points earned by each team groups in different seasons
#using season 1 as an example
ggplot(points_teamgroup("1"),
       mapping = aes(y = reorder(team_group, total_points), x = total_points)) +
  geom_bar(stat = "identity") + 
  labs(
    x = "Total Points", 
    y = "Team Group",
    title = "Total Points Earned By Each Team Group")
```
