---
title: "IDS investigation worksheet"
author: "by Fighting Wolves: Jiayi Wan, Wanfang Zhen, George Zhu, Yifu Li & Yunrui Lyu"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidymodels)
```


```{r load-data}
FERR0 <- read_csv("data/formula_e_race_results.csv")
#the original dataset
FERR <- read_csv("data/formula_e_race_results.csv") %>% 
  # Removing rows where points is 0
  filter(points != 0)
problems()
View(FERR)
View(FERR0)
```


```{r summary of best drivers}
# Calculate total points for each driver over each season
driver_season_points <- FERR %>%
  group_by(season, driver) %>%
  summarise(total_points = sum(points), .groups = 'drop')

# Find the driver with the best total points for each season
best_drivers_by_season <- driver_season_points %>%
  group_by(season) %>%
  filter(total_points == max(total_points)) %>%
  ungroup()

# Display the summary table with the best drivers by season and their total points
best_drivers_by_season_summary <- best_drivers_by_season %>%
  select(season, driver, total_points)

best_drivers_by_season_summary

```


```{r list of driver}
points_driver <- function(x){
  result <- 
  FERR %>%
    filter(x == season) %>%
    group_by(driver) %>%
    summarise(total_points = sum(points, na.rm = TRUE)) %>%
    arrange(desc(total_points))
  return(result)
}

for(i in 1:7)
  print (points_driver(i))


```


```{r driver visualization}
ggplot(points_driver("2"), aes(x = reorder(driver, total_points), 
                               y = total_points, 
                               fill = total_points)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = total_points), 
            position = position_dodge(width = 0.9), 
            hjust = -0.1, 
            vjust = 0.25, 
            size = 3) +
  scale_fill_gradient(low = "skyblue", high = "purple") +  # Gradient color based on total points
  labs(
    x = "Driver", 
    y = "Total Points",
    title = "Total Points Earned By Each Driver in Season 1"
  ) +
  theme_minimal() +  # A clean, minimal theme
  theme(
    plot.title = element_text(hjust = 0.5), # Center the title
    axis.text.x = element_text(hjust = 1),  # Rotate x-axis labels for better readability
    legend.title = element_blank() # Remove the legend title
  ) +
  coord_flip() # Flip the coordinates to make a horizontal bar plot

```


```{r}
#frequency
freq <- 
  filter(FERR0, season != "7") %>%
  select(driver)  %>% 
  table()
freq_driver <- as.data.frame(freq)
View(freq_driver)


#filter the frequency 

freq_driver2 <-
  freq_driver %>% filter (freq >= "3")


#frequency in season
freq_season <- FERR0 %>%
  mutate(across(everything(), as.character),
         `Season 1` = if_else(season == "1", 1, 0),
         `Season 2` = if_else(season == "2", 1, 0),
         `Season 3` = if_else(season == "3", 1, 0),
         `Season 4` = if_else(season == "4", 1, 0),
         `Season 5` = if_else(season == "5", 1, 0),
         `Season 6` = if_else(season == "6", 1, 0),
         `Season 7` = if_else(season == "7", 1, 0)) %>%
  group_by(driver) %>%
  summarise(across(`Season 1`:`Season 7`, sum, na.rm = TRUE))

#average
average_driver <- FERR0 %>%
  group_by(driver) %>%
  summarize(avg_points = mean(points, na.rm = TRUE))
#average after filter season7 out
average_driver2 <-
  filter(FERR0, season != 7 ) %>%
  group_by(driver) %>%
  summarize(avg_points = mean(points, na.rm = TRUE))

freq_avg <- full_join(freq_driver, average_driver, by = "driver")
freq_avg2 <- left_join(freq_driver2, average_driver, by = "driver")
freq_avg3 <- left_join(freq_driver2, average_driver2, by = "driver")

#linear regression original model
multi_re_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_points ~ Freq, data = freq_avg)

#r squared model 1
glance(multi_re_fit)$r.squared
multi_re_fit

#linear regression after filter freq >= 3
multi_re_fit2 <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_points ~ Freq, data = freq_avg2)

#r squared model2, indicating an improvement
glance(multi_re_fit2)$r.squared
multi_re_fit2

#linear regression filter freq >= 3 and season != 7
multi_re_fit3 <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_points ~ Freq, data = freq_avg3)
multi_re_fit3

#r squared model3
glance(multi_re_fit3)$r.squared
multi_re_fit3
#visualize model1
model1 <- ggplot(data = freq_avg, aes(x = Freq, y = avg_points)) + 
  geom_point() + 
  geom_smooth(method = "lm",
              se = FALSE)
model1

#visualize model2
model2 <- ggplot(data = freq_avg2, aes(x = Freq, y = avg_points)) + 
  geom_point() + 
  geom_smooth(method = "lm",
              se = FALSE)
model2

#visualize model3
model3 <- ggplot(data = freq_avg3, aes(x = Freq, y = avg_points)) + 
  geom_point() + 
  geom_smooth(method = "lm",
              se = FALSE)

```
