---
title: "IDS investigation worksheet"
author: "by Fighting Wolves: Jiayi Wan, Wanfang Zhen, George Zhu, Yifu Li & Yunrui Lyu"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidymodels)
```

```{r load-data, include=FALSE}
FERR0 <- read_csv("data/formula_e_race_results.csv") %>%
  select(season, race_num, driver, points)
FERR <- FERR0 %>% 
  filter(points != 0)
```

```{r best_drivers_summary}
best_drivers_summary <- FERR %>%
  group_by(season, driver) %>%
  summarise(total_points = sum(points), .groups = 'drop') %>%
  group_by(season) %>%
  slice_max(order_by = total_points, n = 1) %>%
  ungroup() %>%
  select(season, driver, total_points)
best_drivers_summary
```

```{r season_1_data(example)}
season_1 <- FERR0 %>%
  filter(season == 1)
season_1_data <- season_1 %>%
  group_by(driver) %>%
  summarise(
    total_points = sum(points),
    average_points = mean(points),
    frequency = n()
    ) %>%
  arrange(desc(total_points)) 
season_1_data
```

```{r season_1_vidualisation(total_points, average_points, frequency)}
ggplot(season_1_data, aes(x = average_points, y = total_points)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  labs(title = "Total Points vs Average Points",
       x = "Average Points",
       y = "Total Points")

ggplot(season_1_data, aes(x = frequency, y = total_points)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  labs(title = "Total Points vs Frequency",
       x = "Frequency",
       y = "Total Points")

ggplot(season_1_data, aes(x = frequency, y = average_points)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  labs(title = "Average Points vs Frequency",
       x = "Frequency",
       y = "Average Points")

mod_1 <- lm(total_points ~ average_points, data = season_1_data)
summary_1 <- summary(mod_1)
r_squared_1 <- summary_1$r.squared
r_squared_1
mod_2 <- lm(total_points ~ frequency, data = season_1_data)
summary_2 <- summary(mod_2)
r_squared_2 <- summary_2$r.squared
r_squared_2
mod_3 <- lm(average_points ~ frequency, data = season_1_data)
summary_3 <- summary(mod_3)
r_squared_3 <- summary_3$r.squared
r_squared_3
```

```{r model}
#frequency
freq <- 
  select(FERR0, driver)  %>% 
  table()
freq_driver <- as.data.frame(freq)
#frequency in season
freq_season <- FERR0 %>%
  mutate(across(everything(), as.character),
         `Season 1` = if_else(season == "1", 1, 0),
         `Season 2` = if_else(season == "2", 1, 0),
         `Season 3` = if_else(season == "3", 1, 0),
         `Season 4` = if_else(season == "4", 1, 0),
         `Season 5` = if_else(season == "5", 1, 0),
         `Season 6` = if_else(season == "6", 1, 0),
         `Season 7` = if_else(season == "7", 1, 0)) %>%
  group_by(driver) %>%
  summarise(across(`Season 1`:`Season 7`, sum, na.rm = TRUE))
#average

average_driver <- FERR0 %>%
  group_by(driver) %>%
  summarize(avg_points = mean(points, na.rm = TRUE))

freq_avg <- full_join(freq_driver, average_driver, by = "driver")
multi_re_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_points ~ Freq, data = freq_avg)
glance(multi_re_fit)$r.squared
multi_re_fit

ggplot(data = freq_avg, aes(x = Freq, y = avg_points)) + 
  geom_point() + 
  labs(title = "All Seasons",
       x = "Frequency",
       y = "Average Points") +
  geom_smooth(method = "lm",
              se = FALSE)
```

