---
title: "IDS investigation worksheet"
author: "by Fighting Wolves: Jiayi Wan, Wanfang Zhen, George Zhu, Yifu Li & Yunrui Lyu"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidymodels)
```

```{r load-data, include=FALSE}
FERR0 <- read_csv("data/formula_e_race_results.csv") %>%
  select(season, race_num, driver, points)
FERR <- FERR0 %>% 
  filter(points != 0)
```

```{r best_drivers_summary}
best_drivers_summary <- FERR %>%
  group_by(season, driver) %>%
  summarise(total_points = sum(points), .groups = 'drop') %>%
  group_by(season) %>%
  slice_max(order_by = total_points, n = 1) %>%
  ungroup() %>%
  select(season, driver, total_points)
best_drivers_summary
```

```{r season_1_data(example)}
season_1 <- FERR0 %>%
  filter(season == 1)
season_1_data <- season_1 %>%
  group_by(driver) %>%
  summarise(
    total_points = sum(points),
    average_points = mean(points),
    frequency = n()
    ) %>%
  arrange(desc(total_points)) 
season_1_data
```

```{r season_1_vidualisation(total_points, average_points, frequency)}
ggplot(season_1_data, aes(x = average_points, y = total_points)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(title = "Total Points vs Average Points",
       x = "Average Points",
       y = "Total Points")

ggplot(season_1_data, aes(x = frequency, y = total_points)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(title = "Total Points vs Frequency",
       x = "Frequency",
       y = "Total Points")

ggplot(season_1_data, aes(x = frequency, y = average_points)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(title = "Average Points vs Frequency",
       x = "Frequency",
       y = "Average Points")

mod_1 <- lm(total_points ~ average_points, data = season_1_data)
summary_1 <- summary(mod_1)
r_squared_1 <- summary_1$r.squared
r_squared_1
mod_2 <- lm(total_points ~ frequency, data = season_1_data)
summary_2 <- summary(mod_2)
r_squared_2 <- summary_2$r.squared
r_squared_2
mod_3 <- lm(average_points ~ frequency, data = season_1_data)
summary_3 <- summary(mod_3)
r_squared_3 <- summary_3$r.squared
r_squared_3
```

```{r model}
#frequency
freq <- 
  select(FERR0, driver)  %>% 
  table()
freq_driver1 <- as.data.frame(freq)

#average

avg_driver1 <- FERR0 %>%
  group_by(driver) %>%
  summarize(avg_points = mean(points, na.rm = TRUE))

freq_avg1 <- full_join(freq_driver1, avg_driver1, by = "driver")
multi_re_fit1 <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_points ~ Freq, data = freq_avg1)
#r squared of original model
glance(multi_re_fit1)$r.squared

multi_re_fit1

ggplot(data = freq_avg1, aes(x = Freq, y = avg_points)) + 
  geom_point() + 
  labs(title = "All Seasons",
       x = "Frequency",
       y = "Average Points") +
  geom_smooth(method = "lm",
              se = FALSE)

#model 2, 3, 4

#freq filters season != 7 
freq <- 
  filter(FERR0, season != "7") %>%
  select(driver)  %>% 
  table()
freq_driver2 <- as.data.frame(freq)

#freq filters freq >= 3
freq_driver3 <-
  freq_driver1 %>% filter (Freq >= 3)

#freq filters season != 7 and freq >= 3
freq_driver4 <-
  freq_driver2 %>% filter (Freq >= 3)

#average filters season != 7
avg_driver2 <-
  filter(FERR0, season != 7 ) %>%
  group_by(driver) %>%
  summarize(avg_points = mean(points, na.rm = TRUE))


#filters season != 7
freq_avg2 <- left_join(freq_driver2, avg_driver2, by = "driver")
#filters freq >= 3
freq_avg3 <- left_join(freq_driver3, avg_driver1, by = "driver")
#filters freq >= 3 and season != 7
freq_avg4 <- left_join(freq_driver4, avg_driver2, by = "driver")


#fit model 2
multi_re_fit2 <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_points ~ Freq, data = freq_avg2)

#r squared model2, indicating an improvement
glance(multi_re_fit2)$r.squared

multi_re_fit2

#fit model 3
multi_re_fit3 <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_points ~ Freq, data = freq_avg3)

#r squared model3
glance(multi_re_fit3)$r.squared

multi_re_fit3

#fit model 4
multi_re_fit4 <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_points ~ Freq, data = freq_avg4)

#r squared model2, indicating an improvement
glance(multi_re_fit4)$r.squared

multi_re_fit4

#visualize model2
model2 <- ggplot(data = freq_avg2, aes(x = Freq, y = avg_points)) + 
  geom_point() + 
  geom_smooth(method = "lm",
              se = FALSE)
model2

#visualize model3
model3 <- ggplot(data = freq_avg3, aes(x = Freq, y = avg_points)) + 
  geom_point() + 
  geom_smooth(method = "lm",
              se = FALSE)
model3

#visualize model 4
model4 <- ggplot(data = freq_avg4, aes(x = Freq, y = avg_points)) + 
  geom_point() + 
  geom_smooth(method = "lm",
              se = FALSE)
model4
```