---
title: "Formula E Championship Predictions"
author: "by Fighting Wolves: Jiayi Wan, Wanfang Zhen, George Zhu, Yifu Li & Yunrui Lyu"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, include = FALSE}
library(tidyverse)
library(dplyr)

```


```{r load-data, include=FALSE}
# load your data here and any pre-processing/cleaning 
#  that you need for your report.

```


## Research Question
The Formula E Championship, notorious for its unpredictability, is influenced by a myriad of factors such as driver expertise, car performance, circuit characteristics, and race formats, all contributing to its unforeseeable outcomes. This report aims to explore the relationship between XXX and XXX in the most impartial manner possible.

The report commences with a concise delineation of the methodology for curating pristine data, coupled with an exposition of the selected statistical models and the pertinent questions they are designed to address. Subsequently, tables, figures, summary values, and fitted models are presented in a clear and explanatory manner. The research then objectively highlights systematic and random errors found in the data, methodology, and practical implications, with proposed ethical solutions for systematic biases. Finally, the report addresses the research objectives and questions, offering responses based on the statistical analysis.



## Data


## Findings
Background and Target:

Research methods and Assumptions:

Outcomes:(clean & tidy data, graphs and tables)

Analysis:

Evaluation and Limitations:

Conclusion:


## References
ABB FIA Formula E World Championship, S n.d.,RULES AND REGULATION, FIA Formulae, viewed 30 Nov 2023, <https://www.fiaformulae.com/en/championship/rules-and-regulations#:~:text=Championship%20and%20standings,most%20points%20over%20the%20season.>.

Formula E Chronicles, S n.d., FORMULAE E CHAMPIONS, Formula E Chronicles, viewed 30 Nov 2023, <https://formulaechronicles.com/list-of-formula-e-champions/#:~:text=Points%20are%20awarded%20based%20on,the%20respective%20championship%20or%20trophy>.

Formulae Fandom, S n.d., 2019/20 Formula E Championship, Wiki, viewed 30 Nov 2023, <https://formulae.fandom.com/wiki/2019/20_Formula_E_Championship>.

MLANDRY, S n.d., Formula E Championship, Kaggle, viewed 30 Nov 2023, <https://www.kaggle.com/datasets/mlandry/formula-e-championship>.
