---
title: "Formula E Championship Predictions"
author: "by Fighting Wolves: Jiayi Wan, Wanfang Zhen, George Zhu, Yifu Li & Yunrui Lyu"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, include = FALSE}
library(tidyverse)
library(dplyr)

```


```{r load-data, include=FALSE}
# load your data here and any pre-processing/cleaning 
#  that you need for your report.

```


## Research Question
In the “Formula E Championship Predictions" research, we mainly explore and predict which driver and team is most likely to win the championship.Therefore, this study will focus on which drivers and teams have performed best over the past seven seasons.

The Formula E racing championship is notoriously unpredictable due to differences between drivers, cars, formats，venues and so on. This sparked our interest in finding drivers or teams that are absolutely dominant, allowing us to ignore potential disadvantages and unfairness in the competition during our research.


## Data


## Findings
Background and Target:

Research methods and Assumptions:

Outcomes:(clean & tidy data, graphs and tables)

Analysis:

Evaluation and Limitations:

Conclusion:


## References
Formula E Chronicles, “DRIVERS” [online]. 
Available at:https://formulaechronicles.com/list-of-formula-e-champions/#:~:text=Points%20are%20awarded%20based%20on,the%20respective%20championship%20or%20trophy (Accessed:16-11-2023)
Kaggle, "Formula E Championship" [online]. 
Available at:https://www.kaggle.com/datasets/mlandry/formula-e-championship (Accessed:16-11-2023)

Fluker, M 2017, Fluker posts: community based environmental monitoring, electronic dataset, Fluker Post Research Project, viewed 12 June 2018, <http://www.flukerpost.com>. (citation example)

